Spectroscopic Characterization of New Er$^{3+}$ Host Crystals for Quantum Network Applications

### 2020-04-05 Draft.tex
Finish "a brief history of qc"

\item \listheader{Nuclear magnetic resonance (NMR) quantum computers} use the nuclear spins of atoms or molecules dissolved in solution as the qubit \cite{Cory1997}. Unfortunately, it was shown after a few seemingly successful bulk NMR demonstrations that no entanglement had actually occurred in these experiments, and that entangelement is a necessary part of most important quantum algorithms \cite{Braunstein1999,Linden2001}.

\item \listheader{Solid-state atoms and atom-like defects} such as rare earth ions or nitrogen-vacancy (NV) centers in crystals are in some sense descendents of NMR-based quantum computing paradigms \notetoself{[?]}. In these systems, the spin states of valence electrons serve as qubits. Light-matter interfaces can be achieved by coupling these atoms with photons at the same energy as an optical transition in the qubit atom \notetoself{[?]}.

@@

\notetoself{At this point, I should debrief the different paradigms, then talk about why we would like telecom single-photon sources, quantum memories, and light-matter interfaces (quantum networks, modular quantum computing, quantum repeaters). What exactly are we proposing to use this system for?}

>>>>

\item \listheader{Nuclear magnetic resonance (NMR) quantum computers} use the nuclear spins of atoms or molecules dissolved in solution as the qubit \cite{Cory1997}. Unfortunately, it was shown after a few seemingly successful bulk NMR demonstrations that no entanglement had actually occurred in these experiments, and that entangelement is a necessary part of most important quantum algorithms \cite{Braunstein1999,Linden2001}. It was also hard to scale these computers, as each extra qubit required the synthesis of a new molecule. However, the legacy of NMR computers lives on, as many current quantum computing schemes (see the next list item) make use of the main ideas of NMR computers.

\item \listheader{Point defects in solid state hosts} such as rare earth ions or nitrogen-vacancy (NV) centers in crystals are in some sense descendents of NMR-based quantum computing paradigms \notetoself{[?]}. In these systems, the spin states of valence electrons serve as qubits. Light-matter interfaces can be achieved by coupling these atoms with photons at the same energy as an optical transition in the qubit atom \notetoself{[?]}.

@@

Although superconducting circuit quantum computers have been the most successful so far in terms of implementing complicated quantum algorithms, they are not useful for quantum networks applications. Linear optical quantum computers are the best suited for working purely with photonic qubits in quantum networks, but without the superior computing power offered by superconducting circuits can only implement fairly simple tasks. Thus, point defects in solid state hosts are a very exciting platform, as they offer the possibility of light-matter interfaces that could marry the power of superconducting circuit computers with the distance allowed by photons. This would enable a variety of exciting quantum technologies, such as quantum cryptography, quantum-enhanced metrology, and modular quantum computing.
